Toward single particle reconstruction without particle picking: Breaking the detection limit

### 2018-09-07 pnas/Towards.tex
Before ;erging of finql pqper concerns in the discussion

% Please add here a significance statement to explain the relevance of your work
\significancestatement{A common states that small molecules cannot be reconstructed using cryo-EM. In this paper, we show that this argument is flaw and show }

% Please include corresponding author, author contribution and author declaration information
\authorcontributions{Please provide details of author contributions here. \revised{Let's leave it open for now} }
\authordeclaration{The authors declare no conflicts of interest.}
%\equalauthors{\textsuperscript{1}A.O.(Author One) and A.T. (Author Two) contributed equally to this work (remove if not applicable).}
\correspondingauthor{\textsuperscript{2}To whom correspondence should be addressed. E-mail: author.two\@email.com}

@@

Beyond data acquisition and computational challenges, there are modeling issues to consider.
As stated, our approach relies on two core assumptions that are not necessarily verified in SPR experiments.
First, we assume an additive white noise model, while in practice the noise may be correlated or signal dependent. To address this point, it may be necessary to investigate better noise models and to incorporate power spectrum estimation methods. % and to extend the autocorrelation analysis accordingly. 
Second, we assume that any two particles are sufficiently separated, and we use this assumption to derive algebraic relations between autocorrelations of the micrographs and autocorrelations of the 3-D volume. 
We believe that this constraint could be replaced by a probabilistic condition on the average number of projections per micrograph.  
%Such a condition can be met in practice by careful experimental design.

@@

@@

% Bibliography
\bibliography{ref}

>>>>

% Please add here a significance statement to explain the relevance of your work
\significancestatement{It is commonly believed that cryo-EM cannot be used to image the 3-D structure of small molecules (below ~50kDa). The classical argument is that, due to the high noise levels in cryo-EM, small particles cannot be detected reliably in micrographs. Challenging that belief, we demonstrate on a mathematical toy model that detection is not a prerequisite for structure reconstruction. Our reconstruction method is based on autocorrelation analysis. It requires only one pass over the data, so that it should, in principle, be appropriate for high-throughput experiments. This autocorrelation approach could also apply to other applications where the goal is estimation rather than detection.
}

% Please include corresponding author, author contribution and author declaration information
\authorcontributions{Please provide details of author contributions here. \revised{Let's leave it open for now} }
\authordeclaration{The authors declare no conflicts of interest.}
%\equalauthors{\textsuperscript{1}A.O.(Author One) and A.T. (Author Two) contributed equally to this work (remove if not applicable).}
\correspondingauthor{\textsuperscript{2}To whom correspondence should be addressed. E-mail: tamir.bendory@princeton.edu}

@@

Beyond data acquisition and computational challenges, there are modeling issues to consider.
As stated, our approach relies on two core assumptions that are not necessarily verified in SPR experiments.
First, we assume an additive white noise model, while in practice the noise may be colored.
In that case, the general strategy would remain the same: establish a forward model expressing the expected autocorrelations of the micrographs in terms of the target volume, its density in the micrograph and the noise statistics (which would now involve more than the single parameter $\sigma^2$).
%To address this point, it may be necessary to investigate better noise models and to incorporate power spectrum estimation methods. % and to extend the autocorrelation analysis accordingly. 
Second, we assume that any two particles are sufficiently separated, and we use this assumption to derive algebraic relations between autocorrelations of the micrographs and autocorrelations of the 3-D volume. 
We believe that this constraint could be replaced by a probabilistic condition on the average number of projections per micrograph.  
%Such a condition can be met in practice by careful experimental design.

@@

\
% Bibliography
\bibliography{ref}

@@
